Long-form recording of infant body position in the home using wearable inertial sensors

### 2023-03-16 manuscript.Rmd
FULL DRAFT

Moreover, real-time recording of motor behavior provides a way to measure how infant motor behavior links to other types of experiences in the moment in daily life. As we reviewed, @MalachowskiSalo2023 used a combination of LENA&reg; and EMA surveys to find that infants heard less adult speech when restrained in seating devices. Combining LENA&reg; and long-form motor recordings can take this a step further by measuring more precisely how speech and body position covary within a day. Synchronizing long form motor recordings to other continuous monitors, such as wearable ECG [@WassPhillips2022] can provide information about how infant arousal relates to motor behavior. "TotTag"---a wearable device for measuring infant-caregiver distance [@SaloPannuto2022]---or caregiver worn activity trackers/physiology monitors could be paired with body position classification to better understand how moment-to-moment interpersonal dynamics relate to infant motor behavior.

@@

## Limitations
- No validation at the end of the day (practically this would be hard to do, syncing a challenge)
- Limited to within the home. Driving/strollers are motion signals we don't have training data for, but this could be added in the future. 
- Relying on CG reports of naps/diaper changes. 
- Bias in training data

@@

>>>>

Moreover, real-time recording of motor behavior provides a way to measure how infant motor behavior links to other types of experiences in the moment in daily life. As we reviewed, @MalachowskiSalo2023 used a combination of LENA&reg; and EMA surveys to find that infants heard less adult speech when restrained in seating devices. Combining LENA&reg; and long-form motor recordings can take this a step further by measuring more precisely how speech and body position co-vary within a day. Synchronizing long form motor recordings to other continuous monitors, such as wearable ECG [@WassPhillips2022] can provide information about how infant arousal relates to motor behavior. "TotTag"---a wearable device for measuring infant-caregiver distance [@SaloPannuto2022]---or caregiver worn activity trackers/physiology monitors could be paired with body position classification to better understand how moment-to-moment interpersonal dynamics relate to infant motor behavior.

@@

## Limitations

We acknowledge several limitations in the current approach. First, a stronger test of full-day accuracy would be to compare accuracy at the start of the recording period to accuracy at the end, rather than using the distal comparison video that followed the first 90 minutes of the study. As we described in the procedure section, synchronizing video cameras and inertial sensors required capturing a synchronization point on video. We completed this procedure prior to giving equipment to caregivers so that they were not responsible for synchronization; in fact, caregivers never touched a button on the video cameras. An end-of-day video would require a lot on the part of caregivers, and any mistakes in the procedure would lead to misaligned and unusable data. Given that most recordings ended at infants' bedtimes, having an experimenter visit families in the evening to video record would be intrusive.

Second, we relied on caregiver logs of infants' naps and times when sensors were removed to separate usable data (times when infants wore the sensors while awake) from unusable data. Although most caregivers were diligent about completing logs, there were a few cases that caregivers may have failed to report naps (younger infants \#1 and \#4). In the future, algorithms can be developed to automatically identify periods of sleep and times when sensors are off the body. Such algorithms exist for adults using wrist-worn sensors, however, we did not use them because they have not been validated for infant participants wearing sensors on hips/ankles. Differences in infants' positioning while asleep (held in caregivers arms, laying in cribs, reclined in strollers and carseats) might make classifying sleep more difficult compared with adults based on movement. 
<!-- NEED SLEEP AND WEAR TIME CITES> -->
<!-- Algorithms for infant sleep? -->

Third, although the goal was to collect fully naturalistic behavior, we opted to restrict recording to times when participants were in the home. Inertial sensors can travel with participants, and there is no doubt that infants could have worn the sensors out of the home on errands. However, we do not yet have training data to detect periods of transportation (e.g., moving in a car or in a stroller) that might add noise and/or lead to misclassification of body positions. Future work should aim to collect data in these scenarios so that body position can be captured in or out of the home.

@@

In summary, the current study demonstrates the validity of long-form recordings of infant motor behavior in the home. Our analyses show that body position classifications---whether infants are supine, prone, sitting, upright, or held---are accurate immediately and even following a substantial delay. Most important, we find substantial agreement between human-coded and model-predicted body position for data collected during truly everyday, unsupervised activities that create the most challenging cases for automatic classification. In most cases, model prediction accuracy approached human reliability, suggesting that model predictions can be confidently used in analyses of full-day infant behavior. Examining the resulting corpus of `r apa_num(sum(coverage$hours_recorded))` hours of real-time infant body position showed the feasibility of capturing data covering the majority of infants' awake time and the variety of activities contained therein. A rudimentary analysis of aggregated data showed that full-day position estimates conformed to expectations about age differences in motor behavior. Future work employing the method can go beyond aggregated measures of behavior to uncover the temporal structure in infants' daily motor experiences.

### 2023-03-16 manuscript.tex
FULL DRAFT

Moreover, real-time recording of motor behavior provides a way to measure how infant motor behavior links to other types of experiences in the moment in daily life. As we reviewed, Malachowski et al. (2023) used a combination of LENA® and EMA surveys to find that infants heard less adult speech when restrained in seating devices. Combining LENA® and long-form motor recordings can take this a step further by measuring more precisely how speech and body position covary within a day. Synchronizing long form motor recordings to other continuous monitors, such as wearable ECG (Wass et al., 2022) can provide information about how infant arousal relates to motor behavior. ``TotTag''---a wearable device for measuring infant-caregiver distance (Salo et al., 2022)---or caregiver worn activity trackers/physiology monitors could be paired with body position classification to better understand how moment-to-moment interpersonal dynamics relate to infant motor behavior.

@@

More easily shareable data (non-identifiable, text based)

@@

\begin{itemize}
\tightlist
\item
  No validation at the end of the day (practically this would be hard to do, syncing a challenge)
\item
  Limited to within the home. Driving/strollers are motion signals we don't have training data for, but this could be added in the future.
\item
  Relying on CG reports of naps/diaper changes.
\item
  Bias in training data
\end{itemize}

@@

>>>>

Moreover, real-time recording of motor behavior provides a way to measure how infant motor behavior links to other types of experiences in the moment in daily life. As we reviewed, Malachowski et al. (2023) used a combination of LENA® and EMA surveys to find that infants heard less adult speech when restrained in seating devices. Combining LENA® and long-form motor recordings can take this a step further by measuring more precisely how speech and body position co-vary within a day. Synchronizing long form motor recordings to other continuous monitors, such as wearable ECG (Wass et al., 2022) can provide information about how infant arousal relates to motor behavior. ``TotTag''---a wearable device for measuring infant-caregiver distance (Salo et al., 2022)---or caregiver worn activity trackers/physiology monitors could be paired with body position classification to better understand how moment-to-moment interpersonal dynamics relate to infant motor behavior.

@@

@@

We acknowledge several limitations in the current approach. First, a stronger test of full-day accuracy would be to compare accuracy at the start of the recording period to accuracy at the end, rather than using the distal comparison video that followed the first 90 minutes of the study. As we described in the procedure section, synchronizing video cameras and inertial sensors required capturing a synchronization point on video. We completed this procedure prior to giving equipment to caregivers so that they were not responsible for synchronization; in fact, caregivers never touched a button on the video cameras. An end-of-day video would require a lot on the part of caregivers, and any mistakes in the procedure would lead to misaligned and unusable data. Given that most recordings ended at infants' bedtimes, having an experimenter visit families in the evening to video record would be intrusive.

Second, we relied on caregiver logs of infants' naps and times when sensors were removed to separate usable data (times when infants wore the sensors while awake) from unusable data. Although most caregivers were diligent about completing logs, there were a few cases that caregivers may have failed to report naps (younger infants \#1 and \#4). In the future, algorithms can be developed to automatically identify periods of sleep and times when sensors are off the body. Such algorithms exist for adults using wrist-worn sensors, however, we did not use them because they have not been validated for infant participants wearing sensors on hips/ankles. Differences in infants' positioning while asleep (held in caregivers arms, laying in cribs, reclined in strollers and carseats) might make classifying sleep more difficult compared with adults based on movement.

Third, although the goal was to collect fully naturalistic behavior, we opted to restrict recording to times when participants were in the home. Inertial sensors can travel with participants, and there is no doubt that infants could have worn the sensors out of the home on errands. However, we do not yet have training data to detect periods of transportation (e.g., moving in a car or in a stroller) that might add noise and/or lead to misclassification of body positions. Future work should aim to collect data in these scenarios so that body position can be captured in or out of the home.

@@

In summary, the current study demonstrates the validity of long-form recordings of infant motor behavior in the home. Our analyses show that body position classifications---whether infants are supine, prone, sitting, upright, or held---are accurate immediately and even following a substantial delay. Most important, we find substantial agreement between human-coded and model-predicted body position for data collected during truly everyday, unsupervised activities that create the most challenging cases for automatic classification. In most cases, model prediction accuracy approached human reliability, suggesting that model predictions can be confidently used in analyses of full-day infant behavior. Examining the resulting corpus of 201.06 hours of real-time infant body position showed the feasibility of capturing data covering the majority of infants' awake time and the variety of activities contained therein. A rudimentary analysis of aggregated data showed that full-day position estimates conformed to expectations about age differences in motor behavior. Future work employing the method can go beyond aggregated measures of behavior to uncover the temporal structure in infants' daily motor experiences.
